HiC Contact Map Comaprison Using Graphlet Approach

### 2018-03-27 papers/manuscripts/manuscript.tex
modified graph in the manuscript

@@

The authors of \cite{di2010fast} generalized the idea of graphlets to 
ordered graphs were the nodes are labeled in ascending order.
As can be viewed, there are a total of 14 orbits for graphlets of size
2 and 3 since the label of graphlets is also included in toplogy.
In the new definition, $d_v^i$ denotes the number of orbit $i$ touches 
node $v$. Each node, is then assigned a vector of length 14 
\footnote{number of orbits in graphlets of size 2 and 3}
$(d_v^1, d_v^2, ..., d_v^{14})$ 
and similarity of two nodes in two contact maps can be compared by
how geometrically close their corresponding vectors are.
\section{Materials and Methods}
\subsubsection{Notations}
In this paper, matrices and vectors are represented as bold
capital and bold small letters respectively.
matrix rows and columns are represented by a \textit{dot}
notation. For example, the $i$th row of matrix $M$ is
denoted by $M_{i.}$ and its $j$th column is represented
by $M_{.j}$.

@@

We denote the number of loci in a chromosome $i$ by $N_i$.
The set of all loci involved in contact map $C_{ij}$ is denoted 
by $V_{ij}$.
In intra-chromosomal contact maps, $V_{i,i}$ containts only the 
loci of that particular chromosome ($|V_i| = N_i$), while in 
inter-chromosomal contact maps $V_{ij}$ contains the loci in
the both of chromosomes involved ($|V_{ij}| = N_i + N_j$).

@@

\bibliography{lit}
\bibliographystyle{unsrt}
\end{document}

>>>>

\usepackage{tikz}
\usetikzlibrary{shapes}
\usetikzlibrary{positioning}
\usetikzlibrary{arrows}
\usetikzlibrary{fit}
\usetikzlibrary{decorations.pathreplacing}
\usetikzlibrary{shadows.blur}
\usetikzlibrary{shapes.symbols}

@@

The authors of \cite{di2010fast} generalized the idea of graphlets to 
ordered graphs were the nodes are labeled in ascending order.
As can be viewed, there are a total of 14 orbits for graphlets of size
2 and 3 since the label of graphlets is also included in toplogy.
In the new definition, $d_v^i$ denotes the number of orbit $i$ touches 
node $v$. Each node, is then assigned a vector of length 14 
\footnote{number of orbits in graphlets of size 2 and 3}
$(d_v^1, d_v^2, ..., d_v^{14})$ 
and similarity of two nodes in two contact maps can be compared by
how geometrically close their corresponding vectors are.
\section{Materials and Methods}
\subsubsection{Notations}
In this paper, matrices and vectors are represented with bold
capital and bold small letters respectively.
matrix rows and columns are represented by a \textit{dot}
notation. For example, the $i$th row of matrix $M$ is
denoted by $M_{i.}$ and its $j$th column is represented
by $M_{.j}$.

@@

We denote the number of loci in a chromosome $i$ by $N_i$.
The set of all loci involved in contact map $C_{ij}$ is denoted 
by $\mathbb{V}_{ij}$.
In intra-chromosomal contact maps, $\mathbb{V}_{i,i}$ containts only the 
loci of that particular chromosome ($|\mathbb{V}_i| = N_i$), while in 
inter-chromosomal contact maps $\mathbb{V}_{ij}$ contains the loci in
the both of chromosomes involved ($|\mathbb{V}_{ij}| = N_i + N_j$).

@@

%\begin{tikzpicture}
%    \node [] (a) at (0, 0) {
%        $\begin{pmatrix}  
%            C_{\scriptscriptstyle 1,1,1,1}     &   C_{\scriptscriptstyle 1,1,1,1}  & \cdots    &    C_{\scriptscriptstyle 1,1,1,N_1} \\
%            C_{\scriptscriptstyle 1,1,2,1}     &                &                  &      \\
%            \vdots                             &                & \ddots           &      \\
%            C_{\scriptscriptstyle 1,1,N_1,1}   &                &                  &    C_{\scriptscriptstyle 1,1,N_1, N_1} 
%        \end{pmatrix}$
%    };
%    \node [] (b) [left=1pt of a] {$N_1$};
%    \node [] (c) [above=1pt of a] {$N_1$};
%\end{tikzpicture}
\bibliography{lit}
\bibliographystyle{unsrt}
\end{document}
